---
title: "team project"
output: html_document
---
### read data , coloration analysis and new variable    
```{r}
df <- read.csv("insurance.csv")
cor(df[,c(1,3,4,7)])#relative strong relationship:aage & bmi,charges & age,charges & bmi
pairs(df[,c(1,3,4,7)])
df[df$bmi <30,"weight_status"] ="not obses"
df[df$bmi>=30,"weight_status"] ="obese"
df$weight_status <- as.factor(df$weight_status)
str(df)
```
### categorical variable analysis      
```{r}
library(ggplot2)
ggplot(df,aes(x=region,y=charges))+geom_boxplot()
ggplot(df,aes(x=factor(children),y=charges))+geom_boxplot()
ggplot(df,aes(x=weight_status,y=charges))+geom_boxplot()
ggplot(df,aes(x=smoker,y=charges))+geom_boxplot()
```

### use BIC,cp, AIC to find model     
##### BIC       
```{r}
library(leaps)
library(ggplot2)
full_model<-regsubsets(charges~.+age:sex+age:bmi+age:children+age:smoker+age:region+age:weight_status+sex:bmi+sex:children+sex:smoker+sex:region+sex:weight_status+bmi:children+bmi:smoker+bmi:region+children:smoker+children:region+children:weight_status+smoker:region+smoker:weight_status, data=df,nvmax=38)
model_result = summary(full_model)
lm_full<-lm(charges~.+age:sex+age:bmi+age:children+age:smoker+age:region+age:weight_status+sex:bmi+sex:children+sex:smoker+sex:region+sex:weight_status+bmi:children+bmi:smoker+bmi:region+children:smoker+children:region+children:weight_status+smoker:region+smoker:weight_status, data=df)
```

```{r}
model_bic <- data.frame(submodel=factor(1:38), bic=model_result$bic)
model_bic[which.min(model_bic$bic),"submodel"]
ggplot(model_bic, aes(submodel,bic,group=1))+geom_point(color="blue",size=1)+geom_line(size=1,color="red")+labs(title = "BIC for model")
```
    
the full model with interactction has 38 variables, and model with 5 variable has the lowest BIC.
   
```{r}
forward_model = regsubsets(charges~.+age:sex+age:bmi+age:children+age:smoker+age:region+age:weight_status+sex:bmi+sex:children+sex:smoker+sex:region+sex:weight_status+bmi:children+bmi:smoker+bmi:region+children:smoker+children:region+children:weight_status+smoker:region+smoker:weight_status, data=df,nvmax=38,method = "forward")
backward_model = regsubsets(charges~.+age:sex+age:bmi+age:children+age:smoker+age:region+age:weight_status+sex:bmi+sex:children+sex:smoker+sex:region+sex:weight_status+bmi:children+bmi:smoker+bmi:region+children:smoker+children:region+children:weight_status+smoker:region+smoker:weight_status, data=df,nvmax=38,method = "backward")
```

```{r}
forward_result = summary(forward_model)
forward_result
```

```{r}
backward_result = summary(backward_model)
backward_result
```

according to the forward_result and backward_result , choose the variable   
age,children,bmi:regionsouthwest,bmi:smokeryes and smokeryes:weight_statusobese   

```{r}
modelfrombic<-lm(charges~age+children+bmi:region+bmi:smoker+smoker:weight_status,data=df)

```

##### CP

```{r}
model_cp <- data.frame(submodel=factor(1:38), cp=model_result$cp)
model_cp[which.min(model_cp$cp),"submodel"]
ggplot(model_cp, aes(submodel,cp,group=1))+geom_point(color="blue",size=1,)+geom_line(size=1,color="red")+labs(title = "Cp for model")
```
   
According to plot, the model with 9 variable has the lowest CP.    
###### CPFORWARD           
```{r}
model_cp_forward<-lm(charges~age+sex+children+region+age:region+age:bmi+bmi:smoker+bmi:region+smoker:weight_status,data=df)

```
###### CPBACKWARD         
```{r}
model_cp_backward<-lm(charges~age+sex+children+age:bmi+age:region+bmi:smoker+smoker:weight_status,data=df)

```

##### AIC 

```{r}
step(lm_full,direction = "both")
step(lm_full,direction = "forward")
step(lm_full,direction = "backward")
```

```{r}
model_step <- lm(charges ~ age + sex + bmi + children + smoker + region + weight_status + bmi:smoker + bmi:region + smoker:weight_status,df)
```
##### check BIC and AIC for four model    
```{r}
bic_cp_back <- BIC(model_cp_backward)
bic_cp_for <- BIC(model_cp_forward)
bic_modelfrombic <- BIC(modelfrombic)
bic_step <- BIC(model_step)
bic <- c(bic_cp_back,bic_cp_for,bic_modelfrombic,bic_step)
names(bic) <- c("model_cp_backward","model_cp_forward","modelfrombic","model_step")
bic
```

```{r}

aic_cp_back <- AIC(model_cp_backward)
aic_cp_for <- AIC(model_cp_forward)
aic_modelfrombic <- AIC(modelfrombic)
aic_step <- AIC(model_step)
aic <- c(aic_cp_back,aic_cp_for,aic_modelfrombic,aic_step)
names(aic) <- c("model_cp_backward","model_cp_forward","modelfrombic","model_step")
aic
```
After check BIC and AIC ,the best model is  model_step. 

### using risidual plot to check the model  and model optimization 
```{r}
plot(modelfrombic)#may have some nonlinear relationship
```
        
###### check the new model with nonlinear relationship   
```{r}
test_model <- lm(charges~poly(age,2)+poly(children,3)+bmi:region+bmi:smoker+smoker:weight_status,df)
summary(test_model)
second_model <- lm(charges~poly(age,2)+children+bmi:region+bmi:smoker+smoker:weight_status,df)
summary(second_model)
AIC(second_model)# min
AIC(test_model)
aic_modelfrombic
BIC(second_model)#min 
BIC(test_model)
bic_modelfrombic
```
   
the new model have lowest AIC and BIC            

### model volidation   
```{r}
#volidation
library(caret)
set.seed(350) 
n <-  ceiling(0.75*length(df$charges))# samples
result <- NULL
for (i in 1:5){
training_samps = sample(c(1:length(df$charges)),n)# sampled cases
train_data <- df[training_samps, ]# tranning data
test_data <- df[-training_samps,]
final_model <- lm(charges~poly(age,2)+children+bmi:region+bmi:smoker+smoker:weight_status,train_data)
yhat <- predict(final_model ,newdata = test_data)
R2 = R2(yhat, test_data$charges)
RMSPE = RMSE(yhat, test_data$charges)
MAPE = MAE(yhat, test_data$charges)
RMSPE_N = RMSPE/sd(test_data$charges)
result <- rbind(result,c( i,R2,RMSPE,MAPE,RMSPE_N))}
result <- as.data.frame(result)
names(result) <- c("index","R2","RMSPE","MAPE","RMSPE_N")
result
```
  
### the final model & residual plot
```{r}
summary(second_model)
plot(second_model)
```


